Hector Permafrost

### 2019-09-13 analysis/paper/paper.Rmd
Save more figures as PNG to speed up build

```{r fig-global-scatter, fig.cap = global_scatter_cap, fig.dim = c(8, 5)}
global_scatter_cap <- paste(
  htmlfig(),
  "Hector outputs at 2100 as a function of input parameter values."
)
readd(scatter_lastyear_global_sims)
```

@@

```{r fig-biome-scatter, fig.cap = biome_scatter_cap, fig.dim = c(8, 8)}
biome_scatter_cap <- paste(
  htmlfig(),
  "Hector outputs (with permafrost biome) at 2100 as a function of input parameter values."
)
readd(scatter_lastyear_biome_sims)
```

@@

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions for global Hector."
)
# readd(draws_global_sims)
fig("global_draws.png")
```

@@

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions for Hector with biomes."
)
# readd(draws_biome_sims)
fig("biome_draws.png")
```

>>>>

```{r fig-global-scatter, fig.cap = global_scatter_cap}
global_scatter_cap <- paste(
  htmlfig(),
  "Hector outputs at 2100 as a function of input parameter values."
)
fig("global-scatter.png")
```

@@

```{r fig-biome-scatter, fig.cap = biome_scatter_cap, fig.dim = c(8, 8)}
biome_scatter_cap <- paste(
  htmlfig(),
  "Hector outputs (with permafrost biome) at 2100 as a function of input parameter values."
)
fig("biome-scatter.png")
```

@@

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions for global Hector."
)
fig("global_draws.png")
```

@@

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions for Hector with biomes."
)
fig("biome_draws.png")
```
